\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multicol}

\title{Call for Papers: Artificial Intelligence for Healthcare Applications (AIHA 2022)}
\author{}
\date{}

\begin{document}

\maketitle

Most of the medical data collected from healthcare systems are recorded in digital format. The increased availability of these data has enabled a number of artificial intelligence applications. Specifically, machine learning can generate insights to improve the discovery of new therapeutic tools, to support diagnostic decisions, to help in the rehabilitation process, to name a few. Researchers coupled with expert clinicians can play an important role in turning complex medical data (e.g., genomic data, online acquisitions of physicians, medical imagery, etc.) into actionable knowledge that ultimately improves patient care. In the last years, these topics have drawn clinical and machine learning research which ultimately led to practical and successful applications in healthcare. The purpose of this workshop is to present recent advances in artificial intelligence techniques for healthcare applications.

The workshop will be held in conjunction with the International Conference on Pattern Recognition (ICPR 2022), that will be held from 21 to 25 August 2022 in Montr\'{e}al, Canada.

\section*{Topics}
\begin{multicols}{2}
\begin{itemize}[noitemsep,leftmargin=*]
\item Biomedical image analysis;
\item Data analytics for healthcare;
\item Automatic disease prediction;
\item Automatic diagnosis support systems;
\item Genomic and proteomic data analysis;
\item Artificial intelligence for personalized medicine;
\item Machine Learning as tool to support medical diagnoses and decisions;
\item Machine learning on handwriting and eye-tracking traces for diagnosis and rehabilitation;
\item Decoding of neural signal for diagnosis assistance;
\item Physiological signals processing;
\item Gait analysis;
\item Therapy selection;
\item Brain-computer interface for healthcare;
\item Biomechatronics for medicine;
\item Neuromotor rehabilitation.
\end{itemize}
\end{multicols}

\section*{Important Dates}
\begin{tabular}{ll}
Paper submission deadline & April 4th, 2022 \\
Final decision to authors & May 25th, 2022 \\
Camera-ready for proceedings & June 6th, 2022 \\
\end{tabular}

The accepted papers will be included in the ICPR 2022 Conference Proceedings. Authors of AIHA 2020 papers can find complete instructions of how to format their papers here. Papers can be submitted using the EasyChair. We are also negotiating the publication of special issue on relevant journals in the computer science field. Authors of selected papers will be invited to submit an extended version of their papers accepted to AIHA.

\section*{Organizers}
Nicole Dalia Cilia \quad nicoledalia.cilia@unicas.it \\
Francesco Fontanella \quad f.fontanella@unicas.it \\
Claudio Marrocco \quad c.marrocco@unicas.it \\

AIHA WEBSITE

\end{document}